\textsc{RILS}-\textsc{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-27 paper_resources/doc/paper.tex
Appendix A: stylized acc. to Python style

\usepackage{numprint}
\npdecimalsign{.}
\npthousandsep{}

@@

\textsc{RILS-ROLS} algorithm is available for install on the well-known Python package repository \url{https://pypi.org}, so it can be easily installed by typing commands:
\begin{verbatim}
	pip install rils-rols
\end{verbatim}
\textsc{RILS-ROLS} project page is at \url{https://pypi.org/project/rils-rols}. Here, one can find a minimal working example on how-to-use \textsc{RILS-ROLS}:

\begin{verbatim}
from rils_rols.rils_rols import RILSROLSRegressor
from math import sin, log

@@

# applies the model to a list of input vectors
X_test = [[4, 4], [3, 3]]
y_test = regr.predict(X_test)
print(y_test) 
\end{verbatim}

Python sources, experimental results and all other \textsc{RILS-ROLS} resources can be found at the project GitHub page \url{https://github.com/kartelj/rils-rols}.

>>>>

\usepackage{numprint}
\npdecimalsign{.}
\npthousandsep{}
\usepackage{pythonhighlight}

@@

\textsc{RILS-ROLS} algorithm is available for install on the well-known Python package repository \url{https://pypi.org}, so it can be easily installed by typing commands:
\begin{python} 
	pip install rils-rols
\end{python}
\textsc{RILS-ROLS} project page is at \url{https://pypi.org/project/rils-rols}. Here, one can find a minimal working example on how-to-use \textsc{RILS-ROLS}:

\begin{python}
from rils_rols.rils_rols import RILSROLSRegressor
from math import sin, log

@@

# applies the model to a list of input vectors
X_test = [[4, 4], [3, 3]]
y_test = regr.predict(X_test)
print(y_test) 
\end{python}

Python sources, experimental results and all other \textsc{RILS-ROLS} resources can be found under the project GitHub page \url{https://github.com/kartelj/rils-rols}.
